### 2016-07-05 introduction.tex
edits to abstract and intro

%%%SJ: tried to tighten this paragraph; the original now commented seemed overly
%%complicated
Recent results on reasoning about application invariants in the
presence of weak consistency~\cite{burckhardt14, redblueosdi,
  redblueatc, ecinec, gotsmanpopl16} address broadly related concerns.
Weak consistency is a phenomenon that manifests on replicated data
stores, where operations are concurrently executed against different
replicas, resulting in an execution order inconsistent with any serial
(sequentially consistent) ordering.  In contrast, weak isolation is a
property of atomic transactions whose effects interfere with one
another in ways inconsistent with serializability.  Unlike weak
consistency, weak isolation can manifest even in an unreplicated
setting, as evident from the support for weakly-isolated transactions
on conventional (unreplicated) databases as mentioned above.  With the
added complexity of replication, richer mechanisms are needed to
reason about weak isolation in tandem with weak consistency. Thus,
frameworks for reasoning about weak isolation will necessarily have to
generalize the reasoning frameworks developed for weak consistency in
new and important ways.

>>>>

%%%SJ: tried to tighten this paragraph; the original now commented seemed overly
%%complicated
Recent results on reasoning about application invariants in the
presence of weak consistency~\cite{burckhardt14, redblueosdi,
  redblueatc, ecinec, gotsmanpopl16} address broadly related concerns.
Weak consistency is a phenomenon that manifests on replicated data
stores, where operations are concurrently executed against different
replicas, resulting in an execution order inconsistent with any serial
(sequentially consistent) ordering.  In contrast, weak isolation is a
property of atomic transactions whose effects interfere with one
another in ways inconsistent with serializability.  Unlike weak
consistency, weak isolation can manifest even in an unreplicated
setting, as evident from the support for weakly-isolated transactions
on conventional (unreplicated) databases as mentioned above.  In the
presence of replication, however, the interaction between weak
isolation and weak consistency can be subtle and non-trivial.
Understanding weak isolation in these varied contexts thus requires
new insights and substantial generalization of existing techniques.
